The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-25 article.tex
Added two additional keywords
Finetuning things a bit

\begin{keyword}
\kwd{Java}
\kwd{cheminformatics}
\kwd{bioinformatics}
\end{keyword}

@@

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates can optionally identify
  perspective projects, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently consider distinct can be merged
  (Figure~3\ref{fig:stereoprojections}). The perception is based on an algorithm briefly 
  described by \cite{Karapetyan2015}.

@@

  Graph matching of stereochemistry with the described representation is straight forward. Given
  the atom-atom mapping from a query structure to a target molecule, the focus and carriers of 
  the query stereochemistry are mapped to the target. Using the permutation parity of this mapping
  the configurations compared. SMARTS matching requires some special handling for complex cases 
  \cite{May2014_SMARTS}. For canonicalization, a partial canonical ordering is used to assign an 
  absolute label which can then be integrated into the ordering. More detailed descriptions of 
  these algorithms are described in detail in Chapter 6 of \cite{May2015}.

@@

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with this example reaction (see Fig.~\ref{fig:depiction}):

@@

The molfile format is still very popular, despite it being a proprietary
format it has become a de facto standard. The format forms the core of the larger
CTfile family which was originally developed by MDL Information Systems \cite{Dalby92}. The
current format specification is published by BIOVIA and available on 
request \cite{ctfilespec}.

@@

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds \cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure: 8\label{fig:sgroups}). CDK \textbf{2.0} adds 
supports for representation, reading, writing, and depiction.

>>>>

\begin{keyword}
\kwd{Java}
\kwd{cheminformatics}
\kwd{bioinformatics}
\kwd{metabolomics}
\kwd{depiction}
\end{keyword}

@@

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates can optionally identify
  perspective projects, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently consider distinct can be merged
  (Figure~3\ref{fig:stereoprojections}). The perception is based on an algorithm briefly 
  described by~\cite{Karapetyan2015}.

@@

  Graph matching of stereochemistry with the described representation is straight forward. Given
  the atom-atom mapping from a query structure to a target molecule, the focus and carriers of 
  the query stereochemistry are mapped to the target. Using the permutation parity of this mapping
  the configurations compared. SMARTS matching requires some special handling for complex cases 
  \cite{May2014_SMARTS}. For canonicalization, a partial canonical ordering is used to assign an 
  absolute label which can then be integrated into the ordering. More detailed descriptions of 
  these algorithms are described in detail in Chapter~6 of~\cite{May2015}.

@@

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with this example reaction (see Figure~FIXME\ref{fig:depiction}):

@@

The molfile format is still very popular, despite it being a proprietary
format it has become a de facto standard. The format forms the core of the larger
CTfile family which was originally developed by MDL Information Systems~\cite{Dalby92}. The
current format specification is published by BIOVIA and available on 
request~\cite{ctfilespec}.

@@

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds~\cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure~8\label{fig:sgroups}). CDK \textbf{2.0} adds 
supports for representation, reading, writing, and depiction.
